\documentclass[a4paper,11pt]{article}

% --- Page & Fonts (XeLaTeX) ---
\usepackage[margin=1.8cm]{geometry}
\usepackage{fontspec}
\setmainfont{Times New Roman}
\setsansfont{Arial}

% --- Formatting ---
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{array}
\usepackage{parskip}

\hypersetup{colorlinks=true,urlcolor=blue,linkcolor=black}
\setlist[itemize]{leftmargin=1.2em,label=\textbullet,itemsep=4pt,topsep=2pt}
\pagestyle{empty}

% --- Section style: UPPERCASE + rule ---
\newcommand{\sectionhr}[1]{%
  \vspace{6pt}\textbf{\MakeUppercase{#1}}\par
  \vspace{2pt}\hrule\vspace{6pt}
}

% --- Two–column row (left text / right city, date) ---
\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{R}{>{\raggedleft\arraybackslash}m{4.5cm}}
\newcommand{\rightcol}[2]{\begin{tabular}{@{}r@{}} \textbf{#1}\\ #2 \end{tabular}}

% --- Education entry ---
\newcommand{\EduEntry}[5]{%
  \begin{tabularx}{\linewidth}{@{}L R@{}}
    \textbf{#1}\\ {\itshape #2} & \rightcol{#4}{#5}
  \end{tabularx}\par
  #3
  \vspace{6pt}
}

% --- Experience entry ---
\newcommand{\ExpHeader}[4]{%
  \begin{tabularx}{\linewidth}{@{}L R@{}}
    \textbf{#1} & \rightcol{#3}{#4} \\
    \emph{#2} &
  \end{tabularx}\vspace{2pt}
}

\begin{document}

% ================== Header ==================
\begin{center}
  {\LARGE \textbf{Zayn Zheng Zhi}}\par
  3 Fraser St, Level 17, Duo Tower, Singapore \par
  (+65) 8845-3896 \,|\, \href{mailto:zaynfuture0932@gmail.com}{zaynfuture0932@gmail.com} \,|\, \href{https://www.linkedin.com/in/zayn-zheng/}{https://www.linkedin.com/in/zayn-zheng/}
\end{center}

\hrule\vspace{8pt}

% ================== Summary ==================
\sectionhr{Professional Summary}
\emph{10 years of work experience in data, AI and software engineering fields and 5 years experience dedicated to managerial roles.}

\emph{Demonstrated ability to understand complex data sets, extract insights, and provide valuable recommendations.}

\emph{Effective communicator with the ability to work collaboratively with internal stakeholders and external parties.}

\emph{Led teams of up to 15 members across multiple countries in previous roles.}

% ================== Education ==================
\sectionhr{Education}

\EduEntry
  {Northwestern University}
  {Master of Science in Data Science}
  {\begin{itemize}\item Specialization in Artificial Intelligence\end{itemize}}
  {Evanston, IL, United States}
  {December 2028}

\EduEntry
  {The Hong Kong University of Science and Technology (HKUST)}
  {Master of Business Administration (MBA)}
  {\begin{itemize}\item Global Leadership Program\end{itemize}}
  {Hong Kong}
  {June 2026}

\EduEntry
  {The University of Chicago}
  {Professional Education Program}
  {\begin{itemize}\item Artificial Intelligence and Data Science for Leaders\end{itemize}}
  {Chicago, IL, United States}
  {May 2024}

\EduEntry
  {Huazhong University of Science and Technology (HUST)}
  {Bachelor of Engineering in Automation}
  {\begin{itemize}
    \item Specialization in System Engineering (Computer Engineering)
    \item Co-founder of C-Indigo team to develop Android games
  \end{itemize}}
  {Wuhan, Hubei, China}
  {June 2014}

% ================== Skills ==================
\sectionhr{Managerial \& Technical Skills}
\begin{itemize}
  \item People and agile project management.
  \item Critical and analytical thinking.
  \item Machine learning engineering architecture.
  \item Data strategy and management.
  \item GDPR/PDPA Singapore, AI Act.
  \item Vendor management and coordination; model quality and data quality strategy.
  \item \textbf{Application:} Spring Boot, Cloud Foundry (PCF), Jenkins, Quality Gates, JMeter, OpenAPI, PostgresDB, MQ, HashiCorp Vault.
  \item \textbf{Big data:} Spark, Spark ML, Pandas, Impala, Livy, Yarn, Hadoop, Nifi, Splunk, Pytest–PySpark.
  \item \textbf{Deep learning:} TensorFlow, Keras.
  \item \textbf{Cloud Service:} Cloudera (CML, Hue, Spark on K8s), Databricks MLflow, AWS S3, Terraform.
\end{itemize}

% ================== Experience ==================
\sectionhr{Experience}

\ExpHeader
  {Mastercard}
  {Engineering Manager, Data Engineering}
  {Singapore}
  {Sep 2023 -- Present}
\begin{itemize}
  \item Member of Software Engineering Guild and AI \& Data Science Guild. Managed core team of 5; led automated ML and model monitoring pipelines; handled OKRs, talent planning, performance reviews.
  \item Directed AI Governance/Responsible AI services for NA \& EU. Built privacy-compliant pipelines with Legal/Compliance.
  \item Supported GTM solutions (Dynamic Yield, Portfolio Optimizer, Consumer Credit Analytics, Supplier Enablement).
  \item Migrated on-prem prediction workflows to AWS \& Databricks; improved scalability and performance.
  \item Owned MLOps pipeline management for 500+ cardholder models; improved data/model quality and release reliability.
\end{itemize}

\ExpHeader
  {Apple}
  {Data Solutions Lead}
  {Singapore}
  {Jul 2023 -- Sep 2023}
\begin{itemize}
  \item Implemented data integration and warehousing for Global BI; migrated SAP reports to Snowflake \& Tableau across India, Singapore, China.
\end{itemize}

\ExpHeader
  {OKX}
  {Data Architect}
  {Singapore}
  {Dec 2022 -- May 2023}
\begin{itemize}
  \item Supported C-suite data architecture \& digitization; improved lineage/quality/metadata; stabilized commission rebate pipelines.
  \item Built hybrid streaming–batch pipelines; delivered real-time user segmentation for personalization.
\end{itemize}

\ExpHeader
  {Shopee}
  {Data Team Lead}
  {Singapore}
  {May 2019 -- Sep 2022}
\begin{itemize}
  \item Led advertisement data teams (10 SG + 4 BJ); interviews, mentorship, OKR management.
  \item Built real-time ML data engine; implemented Hudi lakehouse (Kappa DW) for near-real-time market DW across SEA \& LATAM.
  \item Developed ads DW, CRM dashboards, merchant analytics; standardized GDPR-aligned data governance.
\end{itemize}

\ExpHeader
  {Alibaba}
  {Engineer II}
  {Hangzhou, China}
  {Apr 2017 -- Feb 2018}
\begin{itemize}
  \item Built seller onboarding/transfer/qualification systems; unified qualification DW across Alibaba, Alipay \& government.
\end{itemize}

\ExpHeader
  {Mogujie}
  {Senior Development Engineer}
  {Hangzhou, China}
  {May 2015 -- Mar 2017}
\begin{itemize}
  \item Built real-time trading data engines; MQ-based order system; ensured consistency in distributed trading systems.
\end{itemize}

\ExpHeader
  {Zhenai.com}
  {Assistant Java Engineer}
  {Shenzhen, China}
  {Jun 2014 -- Apr 2015}
\begin{itemize}
  \item Maintained backend projects (Spring MVC, Hibernate, MySQL, JSP).
\end{itemize}

% ================== Additional ==================
\sectionhr{Additional Information}
\begin{itemize}
  \item Nationalities: Chinese; Singapore PR.
  \item Languages: English, Mandarin Chinese.
  \item Community: Mentor (Mentoring SG Program); Industry Mentor (NTU).
  \item Certifications: PDPA Practitioner (Singapore); Databricks Fundamentals; Databricks Lakehouse Fundamentals; Data Engineering with Databricks; Applied AI with Deep Learning.
\end{itemize}

\end{document}
